Accesible, realistic genome simulation with selection using \stdpopsim

### 2025-03-12 analysis2_manuscript.tex
added DFE method details

    \subsection*{DFE inference}
    \igcomment{I commented all the text that was here because it wasn't relevant to the methods. We might want to add it to the discussion.
    Kirk also noted that a lot of methods-level details are missing:
    how big was the coding sequence length?
    How was demographic inference done for the different models via the different programs?,
    etc.
    Can someone write this up?}

    % We used three software packages to infer the distribution of fitness effects (DFE) from genetic data:
    % \dadicli \citep{Huang2023,kim2017inference}, \polydfe \citep{tataru2020polydfe}, and \grapes \citep{galtier2016adaptive}.
    % Each software package was run using the same set of simulations.
    % For these analyses we used the exon annotations from the human and vaquita porpoise genomes respectively.
    % A key distinction between our analyses and those done in practice
    % is that we have complete knowledge of which sites are under selection in the simulation,
    % thus our inferences is a best case scenario. Empirical inference of the DFE is a much
    % harder problem as some mutations assumed to be free of selection
    % may in reality be under selection. As above, all methods were run using default settings.
    \igcomment{I edited the description below written by Silas. Please check to make sure it's still accurate.}
    As described above, each DFE-inference method scales selection coefficients slightly differently.
    We thus rescaled each program's output to obtain a selection coefficient ($s$) consistent with the one used by \slim.
    The output of \grapes  was scaled by a factor of  $\mu / \theta$,
    and the output of \polydfe was saled by $2 \mu / \theta$, 
    where $\mu$ is the assumed mutation rate and 
    $\theta$ is the population-scaled mutation rate estimated by each method ($\theta = 4N_{e}\mu$).
    \igcomment{Do we really multiple $\alpha$ by $\nu$ in rescaling for \dadicli?}
    For \dadicli, we report $\alpha * \nu / (\theta / (4 \mu L p))$, where
    $\alpha$ and $\nu$ are the inferred shape and rate parameters of the \dadicli's inferred gamma distribution,
    $L$ is the total number of sites available for the analysis,
    $p$ is the proportion of sites under selection.

>>>>

    \subsection*{DFE inference}
    \igcomment{I commented all the text that was here because it wasn't relevant to the methods. We might want to add it to the discussion.
    Kirk also noted that a lot of methods-level details are missing:
    how big was the coding sequence length?
    How was demographic inference done for the different models via the different programs?,
    etc.
    Can someone write this up?}
    % ADK: I've added a section below that describes the DFE inference methods used in this study.

    % We used three software packages to infer the distribution of fitness effects (DFE) from genetic data:
    % \dadicli \citep{Huang2023,kim2017inference}, \polydfe \citep{tataru2020polydfe}, and \grapes \citep{galtier2016adaptive}.
    % Each software package was run using the same set of simulations.
    % For these analyses we used the exon annotations from the human and vaquita porpoise genomes respectively.
    % A key distinction between our analyses and those done in practice
    % is that we have complete knowledge of which sites are under selection in the simulation,
    % thus our inferences is a best case scenario. Empirical inference of the DFE is a much
    % harder problem as some mutations assumed to be free of selection
    % may in reality be under selection. As above, all methods were run using default settings.
    The DFE inference using \dadicli was conducted by first inferring a demographic model from neutral sites,
    using a two epoch demographic model with 100 repeated runs of the optimization procedure.
    \dadicli then proceeds by using a cached strategy wherein we used 2000 points in the $gamma$ distribution.
    Finally, the DFE was inferred using a ratio of non-synonymous to synonymous mutations of 2.31, again with 
    100 repeated runs of the optimization procedure.
    For \polydfe, we used model 'C' which uses a mixture of a gamma distribution and an exponential distribution,
    where the gamma component is used for negatively selected mutations. For optimization we used
    the default BFGS optimizer with the '-e' flag to automatically estimate the initial parameters values.
    For \grapes, we inferred the DFE under the `GammaZero' model, which assumes that selection coefficients
    are drawn from a single gamma distribution. We used the `-no-div-param' flag to disable the use
    of divergence-based parameter estimation. All other settings were left at their default values.
    All methods used the same exon annotations as generated in the simulations. The total number of coding sites
    in the human and vaquita genomes used were 61,644,801 and 31,039513 respectively.

    % ADK: I've added a section below that describes the DFE inference methods used in this study.
    For comparison among methods, estimates were rescaled. 
    As described above, each DFE-inference method scales selection coefficients slightly differently.
    We thus rescaled each program's output to obtain a selection coefficient ($s$) consistent with the one used by \slim.
    The output of \grapes  was scaled by a factor of  $\mu / \theta$,
    and the output of \polydfe was saled by $2 \mu / \theta$, 
    where $\mu$ is the assumed mutation rate and 
    $\theta$ is the population-scaled mutation rate estimated by each method ($\theta = 4N_{e}\mu$).
    For \dadicli, we report $\alpha * \nu / (\theta / (4 \mu L p))$, where
    $\alpha$ and $\nu$ are the inferred shape and rate parameters of the \dadicli's inferred gamma distribution,
    $L$ is the total number of sites available for the analysis,
    $p$ is the proportion of sites under selection.
